\chapter{Conclusion and Outlook}
\label{chp6}

In Chapter \ref{chp3}, a method to efficiently combine motion and appearance information is proposed. The method gives promising results under simple scenarios. To improve the results of Chapter \ref{chp3} on complex scenarios, in Chapter \ref{chp4}, the Hough transform framework is extended to incorporate motion information, and performs well on two datasets. Still the Hough transform framework itself is troublesome when considering about efficiency. This lead to the method of Chapter \ref{chp5}, which is a new voting system, and is very different in the using of visual and spatial information. The method's effectiveness is proven by experiments, and also it is theoretically promising.

Visual object detection by computers is still and, in near future, continues to be a very open problem. A very hopeful effort would be combining motion, appearance and location information of local features in a robust voting system.

This thesis focuses on improving voting-based detection methods's detection performance by fusion of information of different channels. And in practice, the efficiency of voting is an obstacle, which lead to a new efficient voting system. The method of Chapter \ref{chp3} uses voting to summarise local visual and motion patterns. The simple appearance model and the linear assumption for motion make it only suitable for particular application cases. The method performs well in detection thermal features in tunnels. The method of Chapter \ref{chp4} extends the implicit shape model with motion. This method does not have assumptions for motion model, instead, online motion information are used for clustering local visual patterns, which results in better voting results. Though performing promisingly, the method's efficiency is prevented by the time consuming property of voting systems. In Chapter \ref{chp5}, a new voting system is proposed, by proposing new visual-spatial space dividing method for pyramid matching, the speed of voting is highly enhanced.

Thus detection performance is improved by combining motion information with appearance information in voting, and voting efficiency is improved by proposing new voting mechanisms in the thesis.

In future, the method proposed in Chapter \ref{chp5} will be extended to incorporate motion information similarly to the method of Chapter \ref{chp4}. Hopefully, this effort will result in a method which is both efficient and effective in using motion information.

The methods of Chapter \ref{chp3} and Chapter \ref{chp4} improve detection accuracy by combining motion information. And the method in Chapter \ref{chp5} is very efficient in both training and detection. Nowadays, there are large amounts of video data, while it is still difficult for computers to understand the meanings of these videos  or to make  use of the videos. A few projects have started towards this end~\citep{Chen_2013_ICCV,catbrain}. Still these methods are limited on static images, and are not efficient in training. In future, the proposed methods might be good for such projects. 